Example Paper

### 2021-07-07 latex-article/article.tex
Change citation style to econ.bst
Finish change to econ.bst
Add E, P, 1, Cov, Var commands
Fixed obselete package problem with Utopia
Update title page and reorganized preamble

\documentclass[11pt]{article}

\title{\color{navyblue} Example Paper}
\author{\normalsize Kyle Butts\\{\footnotesize Univ. of Colorado, Boulder}}
\date{\footnotesize\today}

@@

% Set-up Bibliography
\addbibresource{references.bib}

@@

% Title Page -------------------------------------------------------------------
\maketitle
\begin{abstract}
    Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\end{abstract}

@@

\begin{theorem}[Example Theorem]\label{residue_thm}
    This is an example theorem \[ 
        y = f(X) + \varepsilon 
    \]
\end{theorem}

\begin{equation}\label{fe_reg}
    y = f(X) + \varepsilon = X \beta + \psi_i + \nu_t + w_{i,t} + \varepsilon_{i,t} 
\end{equation}

\[ 
    \mathbb{E} \left\{ Y_i(1) - Y_i(0) \right\} = \mathbb{P} (\tau \vert D_i = 1) 
\]

@@

@@

% ------------------------------------------------------------------------------
\newpage
\printbibliography%
% ------------------------------------------------------------------------------

>>>>

\documentclass[12pt]{article}

@@

% \maketitle info
\title{Example Paper}
\author{
    \href{https://kylebutts.com/}{Kyle Butts}\thanks{University of Colorado, Boulder. Email: \href{mailto:buttskyle96@gmail.com}{buttskyle96@gmail.com}.} % \ and Other Author
}
\date{\today}

% pdf info
\hypersetup{pdftitle={Example Paper}, pdfauthor={Kyle Butts}}

@@

% Title Page -------------------------------------------------------------------
\maketitle
\begin{abstract}
    Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

    \par~\par\noindent
    JEL-Classification: 
    \par\noindent
    Keywords: 
    \par
\end{abstract}

@@

\begin{theorem}[Example Theorem]\label{residue_thm}
    This is an example theorem \[ 
        \hat{\beta}=\frac{\sum_{\ell}e_{\ell}z_{\ell}y_{\ell}^{\perp}}{\sum_{\ell}e_{\ell}z_{\ell}x_{\ell}^{\perp}}
    \]
\end{theorem}

Example numbered and non-numbered equations
\begin{equation}\label{fe_reg}
    y = f(X) + \varepsilon = X \beta + \psi_i + \nu_t + w_{i,t} + \varepsilon_{i,t} 
\end{equation}

\[ 
    \expec{Y_i(1) - Y_i(0)} = \prob{\tau \ \vert \ \one(D_i = 1)} 
\]

@@

                \\\bottomrule
            \end{tabular}

@@

% ------------------------------------------------------------------------------
\newpage
\bibliography{references.bib}
% ------------------------------------------------------------------------------
